\documentclass[10pt]{article}

\usepackage{pictex, latexsym, graphicx,amsmath,amssymb,amsbsy,amsfonts,amsthm,verbatim}
\usepackage{graphics}
\usepackage{fullpage}
\usepackage{fancyhdr}

\usepackage{algorithm,algorithmic}
\usepackage{multirow}

\setlength{\headheight}{12pt}
\setlength{\voffset}{-0.25in}
\setlength{\headsep}{0.25in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

% Counter for the problems.
\newcounter{problem}
\newcommand{\problem}{\textbf{\refstepcounter{problem}Problem \theproblem.} }

% Macros
\def\vu{\mathbf{u}}
\def\vx{\mathbf{x}}
\def\vb{\mathbf{b}}
\def\vv{\mathbf{v}}
\def\vw{\mathbf{w}}

\renewcommand{\implies}{\rightarrow}
\renewcommand{\lor}{\vee}
\renewcommand{\land}{\wedge}
\newcommand{\xor}{\oplus}
\renewcommand{\iff}{\leftrightarrow}
\newcommand{\TRUE}{\mathbf{T}}
\newcommand{\FALSE}{\mathbf{F}}
\newcommand{\universe}{\mathcal{U}}
\newcommand\R{\mathbb{R}}


% Math commands:
% \forall, \exists

\begin{document}
\pagestyle{fancyplain}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chead{DISCRETE STRUCTURE (CO1007) --- SOLUTION to Homework 02 --- PREDICATE LOGIC \& PROOF}
\textit{\textbf{\underline{Instruction:}} Type your answers to the following questions provided by LaTeX and submit a zipped file (included .pdf and .tex files) to E-learning by group (only 4-5 members in each group). Only team leader will submit it. One page per problem. Please use the solution template provided.}

% ********** GROUP INFO **********

\begin{center}
    \begin{tabular}{|c|c|c|c|}
        \hline 
        \multicolumn{4}{|c|}{\textbf{GROUP ... ---- MEMBER LIST}} \\ 
        \hline 
        \textbf{No.} &\qquad\qquad \textbf{Name}\qquad\qquad\qquad & \qquad\textbf{ID}\qquad\qquad & \qquad\textbf{Role}\qquad\qquad \\ 
        \hline 
        1 &  &  &  \\ 
        \hline 
        2 &  &  &  \\ 
        \hline 
        3 &  &  &  \\ 
        \hline 
        4 &  &  &  \\ 
        \hline 
        5 &  &  &  \\ 
        \hline 
    \end{tabular} 
\end{center}

% ************** PROBLEM 06 *******************
\clearpage
\problem [5pts] A domino is a flat rectangular block the face of which is divided into two square
parts, each part showing from zero to six pips (or dots). Playing a game consists of playing
dominoes with a matching number of pips. Explain why there are 28 dominoes in a complete set.

\bigbreak
\textit{Solution}
\bigbreak

\par Denote $X$ as the number of dominoes in a complete set.
\par Let $f(k) = |S_{k}|$ where $S_{k} = \{(a, k)| a \leq k\}$. \\
$\Rightarrow f(k) = k + 1$ \\
$\Rightarrow X = \sum_{k = 0}^{6} f(k) = \sum_{k = 0}^{6} k + 1 = 1 + 2 + \ldots + 7$ \\
$\Rightarrow X = \dfrac{7 \cdot 8}{2} = 28$


% ************** PROBLEM 07 *******************
\clearpage
\problem [10pts]
\bigbreak
\textit{Solution}
\bigbreak

\begin{enumerate}
    \item How many solutions are there to the equation $x_{1} + x_{2} + x_{3} + x_{4} \leq 20$, where
    $x_{1}, x_{2}, x_{3}, x_{4}$ are non-negative integers? are positive integers?

    \par Rephrase the problem into ``How many ways are there to arrange 3 vertical bars and 
    $\leq 20$ balls together.

    \par Rephrase the problem \textbf{again} into ``How many ways are there to arrange 4 vertical bars
    and \textbf{exactly} 20 balls together."

    \begin{itemize}
        \item Case 1: $x_{1}, x_{2}, x_{3}, x_{4}$ are non-negative integers.\\
        $\Rightarrow$ The vertical bars can be put next to each other.
        \par There are (20 + 4) = 24 objects. Thus, there are 24 positions.
        $\Rightarrow$ There are $C_{4}^{20 + 4} = 10626$ ways to arrange.

        \item Case 2: $x_{1}, x_{2}, x_{3}, x_{4}$ are positive integers.\\
        \par To solve this problem, we set up 4 (ball, bar) pairs (ball first, bar second) to
        guarantee that the bars cannot be next to each other.
        \par There are (20 + 4 - 4) = 20 objects. Thus, there are 20 positions.
        $\Rightarrow$ There are $C_{4}^{20} = 4845$ ways to arrange.
    \end{itemize}

    \item How many solutions are there to the equation $x_{1} + x_{2} + x_{3} + x_{4} = 20$, where
    $x_{1}, x_{2}, x_{3}, x_{4}$ are non-negative integers with $x_{1} \leq 3$, $x_{2} \geq 2$,
    $x_{3} > 4$?

    \par Rephrase the problem into ``How many ways are there to arrange 3 vertical bars and 20 balls
        together" satisfying the mentioned conditions.
    \par Since $x_{2} \geq 2$, we group (2 balls, bar 2) together into group 2 (the balls come first).
    \par Since $x_{3} > 4$, we group (5 balls, bar 3) together into group 3 (the balls come first).
    \par If $x_{1} = i$ ($i \leq 3$), we group ($i$ ball(s), bar 1) together into group 1. (the
        balls come first). Also, \textbf{the position of group 1 has to be fixed on the leftmost
        side} so that the less than sign can be satisfied.
    \par The number of object when $x_{1} = i$ is: 20 + 3 - i - 2 - 5 = 16 - i. In addition, the
        position of group 1 has been fixed. As a result, the number of arrangements is
        $C_{4 - 1}^{16 - i - 1} = C_{3}^{15 - i} $. 
    \par In total, the number of arrangements is:
    \begin{align*}
        \sum_{i = 0}^{3} C_{3}^{15 - i} = C_{3}^{15} + C_{3}^{14} + C_{3}^{13} + C_{3}^{12} = 1325
    \end{align*}

    \item How many ways to arrange 30 marbles in 5 different boxes, so that box 1 has at least 5
        balls, knowing that box 2 and box 3 do not contain more than 6 balls.

    \par Applying the same way of reasoning like question number 2 based on grouping.
        Note that group 2 and 3 are fixed on the leftmost side and always stay next to each other.
        We can come up with the formula:
    \par Number of arrangement
    \begin{align*}
        & \sum_{i = 0}^{6} \sum_{j = 0}^{6} C_{3}^{28 - i - j} \\
        = & \sum_{i = 0}^{6} \bigg[ C_{3}^{28 - i} + C_{3}^{27 - i} + \ldots
        + C_{3}^{22 - i} \bigg] \\
        = & 16436 + 14490 + 12705 + 11074 + 9590 + 8246 + 7035 \\
        = & 79576
    \end{align*}

\end{enumerate}

% ************** PROBLEM 08 *******************
\clearpage
\problem [10pts]
\bigbreak
\textit{Solution}
\bigbreak



\end{document}
