\documentclass[10pt]{article}

\usepackage{pictex, latexsym, graphicx,amsmath,amssymb,amsbsy,amsfonts,amsthm,verbatim}
\usepackage{graphics}
\usepackage{fullpage}
\usepackage{fancyhdr}

\usepackage{algorithm,algorithmic}
\usepackage{multirow}

\setlength{\voffset}{-0.25in}
\setlength{\headsep}{0.25in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

% Counter for the problems.
\newcounter{problem}
\newcommand{\problem}{\textbf{\refstepcounter{problem}Problem \theproblem.} }

% Macros
\def\vu{\mathbf{u}}
\def\vx{\mathbf{x}}
\def\vb{\mathbf{b}}
\def\vv{\mathbf{v}}
\def\vw{\mathbf{w}}

\renewcommand{\implies}{\rightarrow}
\renewcommand{\lor}{\vee}
\renewcommand{\land}{\wedge}
\newcommand{\xor}{\oplus}
\renewcommand{\iff}{\leftrightarrow}
\newcommand{\TRUE}{\mathbf{T}}
\newcommand{\FALSE}{\mathbf{F}}
\newcommand{\universe}{\mathcal{U}}
\newcommand\R{\mathbb{R}}


% Math commands:
% \forall, \exists

\begin{document}
\pagestyle{fancyplain}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chead{DISCRETE STRUCTURE (CO1007) --- SOLUTION to Homework 02 --- PREDICATE LOGIC \& PROOF}
\textit{\textbf{\underline{Instruction:}} Type your answers to the following questions provided by LaTeX and submit a zipped file (included .pdf and .tex files) to E-learning by group (only 4-5 members in each group). Only team leader will submit it. One page per problem. Please use the solution template provided.}

% ********** GROUP INFO **********

\begin{center}
    \begin{tabular}{|c|c|c|c|}
        \hline 
        \multicolumn{4}{|c|}{\textbf{GROUP ... ---- MEMBER LIST}} \\ 
        \hline 
        \textbf{No.} &\qquad\qquad \textbf{Name}\qquad\qquad\qquad & \qquad\textbf{ID}\qquad\qquad & \qquad\textbf{Role}\qquad\qquad \\ 
        \hline 
        1 &  &  &  \\ 
        \hline 
        2 &  &  &  \\ 
        \hline 
        3 &  &  &  \\ 
        \hline 
        4 &  &  &  \\ 
        \hline 
        5 &  &  &  \\ 
        \hline 
    \end{tabular} 
\end{center}



% ********** PROBLEM 01 **********
\clearpage
\problem [10pts] Let $F(x, y)$ be the statement ``$x$ can fool $y$", where the domain consists of all people in the world. Use quantifiers to express each of these statements.

\bigbreak
\textit{Solution:}

\begin{enumerate}
    %1
    \item Everybody can fool Fred.
    
    %2
    \item Evelyn can fool everybody.

    %3
    \item Everybody can fool somebody.

    %4
    \item There is no one who can fool everybody.

    %5
    \item No one can fool both Fred and Jerry.

    %6
    \item There is exactly one person whom everybody can fool.

    %7
    \item No one can fool himself or herself.

    %8
    \item There is someone who can fool exactly one person besides himself or herself.


\end{enumerate}

%---------------------------------------------------------------------------------------------------------------------------------------------------


% ********** PROBLEM 02 **********
\clearpage
\problem [15pts] Use rules of inference to show that if
    $\forall x (P(x) \lor Q(x)),$
    $\forall x (\neg Q(x) \lor S(x)),$
    $\forall x (R(x) \implies \neg S(x)) and$
    $\forall x \neg P(x)$
    are true, then
    $\exists x \neg R(x)$
    is true. \\


\bigbreak
\textit{Solution:} 
%---------------------------------------------------------------------------------------------------------------------------------------------------



% ********** PROBLEM 03 **********
\clearpage
\problem [10pts] Let $L(x, y)$ be the statement $x$ loves $y$, where the domain for both
$x$ and $y$ consists of all people in the world. Translate the following predicate logic into English.\\
\bigbreak
\textit{Solution:} 
\begin{enumerate}
    %1
    \item $\forall x L(x, Jerry)$

    %2
    \item $\forall x \exists y L(x, y)$

    %3
    \item $\exists y \forall x L(x, y)$
        
    %4
    \item $\exists x \neg L(Lydia, x)$

    %5
    \item $\exists x \forall y \neg L(y, x)$

    %6
    \item $\exists x (\forall y L(y, x) \land \forall z (\forall w L(w, z)) \implies z = x)$

\end{enumerate}
%---------------------------------------------------------------------------------------------------------------------------------------------------



% ********** PROBLEM 04 **********
\clearpage
\problem [10pts] For each of these arguments determine whether the argument is correct or incorrect and explain why.

\bigbreak
\textit{Solution:} 

\begin{enumerate}
    %1
    \item Everyone enrolled in the university has lived in a dormitory.
        Mia has never lived in a dormitory.
        Therefore, Mia is not enrolled in the university.

    %2
    \item A convertible car is fun to drive.
        Isaacss car is not a convertible.
        Therefore, Isaacs car is not fun to drive.

    %3
    \item Quincy likess all action movies.
        Quincy likes the movie Eight Men Out.
        Therefore, Eight Men Out is an action movie.

    %4
    \item All lobstermen set at least a dozen traps.
        Hamilton is a lobsterman.
        Therefore, Hamilton sets at least a dozen traps.

\end{enumerate}

%------------------------------------------------------------------------------------------------------------------------------------------------



% ********** PROBLEM 05 **********
\clearpage
\problem [10pts] Express each of these mathematical statements using predicates,
    quantifiers, logical connectives, and mathematical operators, where the domain
    consists of all integers.

\bigbreak
\textit{Solution:} 

\begin{enumerate}
    %1
    \item The product of two negative integers is positive.

    %2
    \item The average of two positive integers is positive.

    %3
    \item The absolute value of the sum of two integers does not exceed the sum of the
        absolute values of the integers.
\end{enumerate}

%------------------------------------------------------------------------------------------------------------------------------------------------


% ********** PROBLEM 06 **********
\clearpage
\problem [15pts] Express each of these mathematical statements using quantifiers.
    Then form the negation of the statement so that no negation is to the left of a quantifier.
    Next, express the negation in simple English.

\bigbreak
\textit{Solution:}

    \begin{enumerate}
        %1
        \item All dogs have fleas. \\
            \textit{Example: } We write this statement as
                $\forall x (D(x) \implies F(x))$
                or
                $\forall x (\neg D(x) \land F(x)).$
                Its negation is
                $\exists x (D(x) \lor \neg F(x)),$
                and in English it translates into "There is a dog that does not have fleas".

        %2
        \item There is a horse that can add.

        %3
        \item Every koala can climb.

        %4
        \item No monkey can speak French.

        %5
        \item There exists a pig that can swim and catch fish.
    \end{enumerate}

\bigbreak
\textit{Solution:}


%------------------------------------------------------------------------------------------------------------------------------------------------


% ********** PROBLEM 07 **********
\clearpage
\problem [10pts] Use rules of inference to prove that \\
    \begin{align}
        \neg t \lor u \\
        r \implies (s \lor t) \\
        (\neg p \lor q) \implies r \\
        \neg (s \lor u) \\
        \cline{1-2}
        \therefore q
    \end{align}

\bigbreak
\textit{Solution:}


% ********** PROBLEM 08 **********
\clearpage
\problem [15pts] Use rules of inference to prove that \\
    \begin{align}
        \forall x \in \R (P(x) \lor Q(x)) \\
        \forall x \in \R (\neg P(x) \land Q(x) \implies T(x)) \\
        \cline{1-2}
        \therefore \forall x \in \R (\neg T(x) \implies P(x))
    \end{align}

\bigbreak
\textit{Solution:}



% ********** PROBLEM 09 **********
\clearpage
\problem [Bonus] Solve as much as you can the exercises in Section 1.4, 1.5, 1.6 in Rosen's
book, 7th ed. The following are recommended:
    \par Section 1.4: 9, 10, 12, 13, 18, 23, 44
    \par Section 1.5: 8, 10, 18, 28, 33, 36, 49
    \par Section 1.6: 3, 9, 16, 19, 22, 24, 34

\bigbreak
\textit{Solution:}

\end{document}
